The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-14 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Updates for table 3, SQL, parts of text

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 mag AB (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 20.21$\pm$0.14 mag AB
  (observed 3 times between MJD=55537 and 55542), meaning that the WFCAM and
  VISTA observations are $\sim4$ years apart.

>>>>

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with
  $\delta$mag$ < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA
  were removed. This selects one quasar with large, $\delta$mag
  $>0.2$mag differences between the WSA and VSA. This is SDSSJ0349+0034
  which has a WSA $K$-band magnitude of 21.03$\pm$0.35 mag AB (observed at
  MJD=54062.4), while for the VSA $K_s$-band this is 20.20$\pm$0.14 mag AB
  (observed 3 times between MJD=55537 and 55542), meaning that the WFCAM and
  VISTA observations are $\sim4$ years apart.
